Program Transformations for miniKanren

### 2020-05-23 papers/miniKanren/text/nonconj.tex
add ref to fig.2

There are several core ideas behind this algorithm.
The first is to select an arbitrary relation to unfold, not necessarily the leftmost which is safe.
The second idea is to use a heuristic which decides if unfolding a relation call can lead to discovery of contradictions between conjuncts which in turn leads to restriction of the answer set at specialization-time \db{(line 14; \code{heuristically\_select\_a\_call} stands for heurictics combination, the exact code is omitted)}.
If those contradictions are found, then they are exposed by considering the conjunction as a whole and substituting the result of the call unfolding back into the conjunction the call was selected from thus \emph{joining} the conjunction back together instead of using \emph{split} as in CPD \db{(lines 15--23)}.
Finally, if the heuristic fails to select a potentially good call, then the conjunction is splitted into individual calls which are driven in isolation and are never joined \db{(line 25)}.

@@

\subsection{Heuristic}

>>>>

There are several core ideas behind this algorithm.
The first is to select an arbitrary relation to unfold, not necessarily the leftmost which is safe.
The second idea is to use a heuristic which decides if unfolding a relation call can lead to discovery of contradictions between conjuncts which in turn leads to restriction of the answer set at specialization-time \db{(line 14; \code{heuristically\_select\_a\_call} stands for heurictics combination, see section~\ref{sec:heurictic} for details)}.
If those contradictions are found, then they are exposed by considering the conjunction as a whole and substituting the result of the call unfolding back into the conjunction the call was selected from thus \emph{joining} the conjunction back together instead of using \emph{split} as in CPD \db{(lines 15--23)}.
Finally, if the heuristic fails to select a potentially good call, then the conjunction is splitted into individual calls which are driven in isolation and are never joined \db{(line 25)}.

@@

\subsection{Heuristic}
\label{sec:heurictic}
